\subsubsection{fusesoc\_info Targets}
\begin{itemize}
\item nexys-a7-100t
	\begin{itemize}
	\item[$\space$] Info: Base for nexys-a7-100t digilent development board builds, do not use.
	\end{itemize}
\item nexys-a7-100t\_secure\_jtag\_io
	\begin{itemize}
	\item[$\space$] Info: Build for nexys-a7-100t digilent development board with PMP enabled Veronica RISCV.
	\end{itemize}
\item nexys-a7-100t\_jtag\_io
	\begin{itemize}
	\item[$\space$] Info: Build for nexys-a7-100t digilent development board with standard Veronica RISCV.
	\end{itemize}
\item nexys-a7-100t\_secure\_jtag\_bscane
	\begin{itemize}
	\item[$\space$] Info: Build for nexys-a7-100t digilent development board with PMP enabled Veronica RISCV.
	\end{itemize}
\item nexys-a7-100t\_jtag\_bscane
	\begin{itemize}
	\item[$\space$] Info: Build for nexys-a7-100t digilent development board with standard Veronica RISCV.
	\end{itemize}
\item nexys-a7-100t\_linux\_jtag\_bscane
	\begin{itemize}
	\item[$\space$] Info: Build for nexys-a7-100t digilent development board with Linux Veronica RISCV.
	\end{itemize}
\item nexys-a7-100t\_linux\_jtag\_bscane\_bootgen
	\begin{itemize}
	\item[$\space$] Info: Build for nexys-a7-100t digilent development board with Linux Veronica RISCV with bootgen for uboot.
	\end{itemize}
\item genesys2
	\begin{itemize}
	\item[$\space$] Info: Base for genesys2 digilent development board builds, do not use.
	\end{itemize}
\item genesys2\_secure\_jtag\_io
	\begin{itemize}
	\item[$\space$] Info: Build for genesys2 digilent development board with PMP enabled Veronica RISCV.
	\end{itemize}
\item genesys2\_jtag\_io
	\begin{itemize}
	\item[$\space$] Info: Build for genesys2 digilent development board with standard Veronica RISCV.
	\end{itemize}
\item genesys2\_secure\_jtag\_bscane
	\begin{itemize}
	\item[$\space$] Info: Build for genesys2 digilent development board with PMP enabled Veronica RISCV.
	\end{itemize}
\item genesys2\_jtag\_bscane
	\begin{itemize}
	\item[$\space$] Info: Build for genesys2 digilent development board with standard Veronica RISCV.
	\end{itemize}
\item genesys2\_linux\_jtag\_bscane
	\begin{itemize}
	\item[$\space$] Info: Build for genesys2 digilent development board with Linux Veronica RISCV.
	\end{itemize}
\item NetFPGA-1G-CML
	\begin{itemize}
	\item[$\space$] Info: Base for NetFPGA-1G-CML digilent development board builds, do not use.
	\end{itemize}
\item NetFPGA-1G-CML\_secure\_jtag\_io
	\begin{itemize}
	\item[$\space$] Info: Build for NetFPGA-1G-CML digilent development board with PMP enabled Veronica RISCV.
	\end{itemize}
\item NetFPGA-1G-CML\_jtag\_io
	\begin{itemize}
	\item[$\space$] Info: Build for NetFPGA-1G-CML digilent development board with standard Veronica RISCV.
	\end{itemize}
\item NetFPGA-1G-CML\_secure\_jtag\_bscane
	\begin{itemize}
	\item[$\space$] Info: Build for NetFPGA-1G-CML digilent development board with PMP enabled Veronica RISCV.
	\end{itemize}
\item NetFPGA-1G-CML\_jtag\_bscane
	\begin{itemize}
	\item[$\space$] Info: Build for NetFPGA-1G-CML digilent development board with standard Veronica RISCV.
	\end{itemize}
\item NetFPGA-1G-CML\_linux\_jtag\_bscane
	\begin{itemize}
	\item[$\space$] Info: Build for NetFPGA-1G-CML digilent development board with Linux Veronica RISCV.
	\end{itemize}
\item kc705
	\begin{itemize}
	\item[$\space$] Info: Base for kc705 xilinx development board builds, do not use.
	\end{itemize}
\item kc705\_secure\_jtag\_bscane
	\begin{itemize}
	\item[$\space$] Info: Build for kc705 xilinx development board with PMP enabled Veronica RISCV.
	\end{itemize}
\item kc705\_jtag\_bscane
	\begin{itemize}
	\item[$\space$] Info: Build for kc705 xilinx development board with standard Veronica RISCV.
	\end{itemize}
\item kc705\_linux\_jtag\_bscane
	\begin{itemize}
	\item[$\space$] Info: Build for kc705 xilinx development board with Linux Veronica RISCV.
	\end{itemize}
\item vc707
	\begin{itemize}
	\item[$\space$] Info: Base for VC707 xilinx development board builds, do not use.
	\end{itemize}
\item vc707\_secure\_jtag\_bscane
	\begin{itemize}
	\item[$\space$] Info: Build for vc707 xilinx development board with PMP enabled Veronica RISCV.
	\end{itemize}
\item vc707\_jtag\_bscane
	\begin{itemize}
	\item[$\space$] Info: Build for vc707 xilinx development board with standard Veronica RISCV.
	\end{itemize}
\item vc707\_linux\_jtag\_bscane
	\begin{itemize}
	\item[$\space$] Info: Build for vc707 xilinx development board with Linux Veronica RISCV.
	\end{itemize}
\item crosslink-nx\_eval
	\begin{itemize}
	\item[$\space$] Info: Defaults for CrossLink NX Evaluation Board, do not use.
	\end{itemize}
\item crosslink-nx\_eval\_jtag\_io
	\begin{itemize}
	\item[$\space$] Info: Build for crosslink-nx\_eval development board with standard Veronica RISCV.
	\end{itemize}
\item crosslink-nx\_eval\_secure\_jtag\_io
	\begin{itemize}
	\item[$\space$] Info: Build for crosslink-nx\_eval development board with secure Veronica RISCV.
	\end{itemize}
\item crosslink-nx\_eval\_linux\_jtag\_io
	\begin{itemize}
	\item[$\space$] Info: Build for crosslink-nx\_eval development board with Linux Veronica RISCV.
	\end{itemize}
\item sim\_cocotb
	\begin{itemize}
	\item[$\space$] Info: Cocotb unit tests
	\end{itemize}
\end{itemize}
